---
title: "Main"
author: "Elizabet Sanyal"
date: "2023-06-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
packages <- c("reticulate", "tensorflow", "abind", "keras", 
              "xts", "PerformanceAnalytics", "kableExtra", 
              "lubridate", "tidyverse", "purrr")
require(packages)
pacman::p_load(reticulate, tensorflow, abind, keras, xts, PerformanceAnalytics, kableExtra, lubridate, tidyverse, purrr, dplyr, tidyr, rlang, furrr)
source("custom_nn_keras.R", local = knitr::knit_global())
source("data_preparation.R", local = knitr::knit_global())
source("model_construction.R", local = knitr::knit_global())
source("backtest.R", local = knitr::knit_global())
```

# Data Preparation
```{r, warning=FALSE, message=FALSE}
load("~/R/Test_GPU/data_ml.RData")
data_ml <- data_ml %>% select(-R3M_Usd,-R6M_Usd,-R12M_Usd)
stock_ids <- levels(as.factor(data_ml$stock_id)) 
stock_days <- data_ml %>%                        
    group_by(stock_id) %>% summarize(nb = n()) 
stock_ids_short <- stock_ids[which(stock_days$nb == max(stock_days$nb))] 

features <- colnames(data_ml[3:95]) 

#Preparing data with stock that have full data (no missing hours)
data_predef_stocks <- process_data(data=data_ml, 
                                   stock_id_column="stock_id",
                                   feature_names=NULL,  
                                   label_name="R1M_Usd", 
                                   use_max_stock_days=TRUE)

data_short_wide <- data_predef_stocks$features_wide
returns_short <- data_predef_stocks$returns_winsorized
returns_short_test <- data_predef_stocks$returns_short_test

#Preparing data with all stock available
data_all_stocks <- process_data(data=data_ml, 
                                stock_id_column="stock_id",
                                feature_names=NULL,  
                                label_name="R1M_Usd", 
                                use_max_stock_days=FALSE)

data_all_wide <- data_all_stocks$features_wide
returns_all <- data_all_stocks$returns_winsorized
returns_all_test <- data_all_stocks$returns

#data_all_wide_imputed <- impute_rowwise(data_all_wide, FUN=median,features)
load("~/R/Deep_Portfolio/data_all_wide_imputed.RData")
returns_all_imputed <- returns_all %>% mutate_all(impute_returns) 


```
# Definition of The Training-Testing-Validation Sample Periods: 
```{r}
num_features <- ncol(data_short_wide)
val_window <- 60
training_window <- 60
first_test <- val_window + training_window
testing_period_len <-  12
testing_periods_seq <- seq(training_window, training_window+testing_period_len)
end_test <- first_test+testing_period_len
#max possible nrow(data_short_wide)-training_window-val_window

```
# Results of The Bayesian Optimisation: Neural Network Parameters
```{r}
activation_nl_i <- "sigmoid"
activation_conc <- "swish"
learning_rate <-0.1
activation_nl_ii <-"tanh"
units_choice <- 1
epochs <- 300
rate <- 0.1
batch_size <- 12
```
# NN with parallell NLinear and Linear Layers
```{r}
illustration_model <- build_model(n_stock_selected, rate, units_choice, 
                         activation_nl_i,activation_conc,learning_rate, 
                         activation_nl_ii, data_wide,sharpe_ratio_loss)
summary(illustration_model)
```
#Backtesting
## Backtesting with predefined stocks with SR loss:

```{r}
backtest_res_predef_ret_sr <- map(testing_periods_seq, backtest, data_short_wide, returns_short, 
                        simple=FALSE, window="expand", stocks_preselected=TRUE, 
                        transaction_cost=FALSE)

test_sample_returns <- as.matrix(returns_short[first_test:end_test,])
weights_predef_sr_expand <- do.call(rbind, lapply(backtest_res_predef_ret_sr, unlist))
test_pf_ret_predef_sr_expand <- rowSums(weights_predef_sr_expand *  test_sample_returns)

#Metrics:
mean(weights_predef_sr_expand)/sd(weights_predef_sr_expand)
```


## Backtesting with predefined stocks with transaction cost adjusted SR loss:
```{r}

backtest_predef_res_sr_tc <- map(testing_periods_seq, backtest, data_short_wide, 
                                 returns_short,simple=FALSE, window="expand", 
                                 stocks_preselected=TRUE, transaction_cost=TRUE)

test_sample_returns <- as.matrix(returns_short[first_test:end_test,])
weights_predef_sr_tc_expand <- do.call(rbind, lapply(backtest_results, unlist))
test_pf_ret_predef_sr_tc_expand <- rowSums(weights_predef_sr_tc_expand *  test_sample_returns)

#Metrics:
mean(test_pf_ret_predef_sr_tc_expand)/sd(test_pf_ret_predef_sr_tc_expand)
```


## Backtesting with all stocks avaible with SR loss:
```{r}
backtest_all_res_sr <- map(testing_periods_seq, backtest, data_all_wide_imputed, 
                                 returns_all_imputed,simple=FALSE, window="expand", 
                                 stocks_preselected=FALSE, transaction_cost=FALSE)

weights_all_res_sr <- do.call(rbind, lapply(backtest_all_res_sr, unlist)) 

test_sample_returns_all <- as.matrix(returns_all_imputed[first_test:end_test,])
test_sample_returns_all[is.na(test_sample_returns_all)] <- 0
test_pf_all_res_sr <- rowSums(weights_all_res_sr *  test_sample_returns_all)
mean(test_pf_all_res_sr)/sd(test_pf_all_res_sr)
```


