---
title: "Main"
author: "Elizabet Sanyal"
date: "2023-06-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(reticulate, tensorflow, abind, keras, xts, PerformanceAnalytics, kableExtra, lubridate, tidyverse, purrr, dplyr, tidyr, rlang, furrr,kerastuneR, lmtest,sandwich, gridExtra,R6)


source("custom_nn_keras.R", local = knitr::knit_global())
source("data_preparation.R", local = knitr::knit_global())
source("model_construction.R", local = knitr::knit_global())
source("backtest.R", local = knitr::knit_global())
source("performance_metrics.R", local = knitr::knit_global())
```

# Data Preparation


## Data Preparation

```{r, warning=FALSE, message=FALSE}
load("~/R/Test_GPU/data_ml.RData")

inputlist <- c("F-F_Research_Data_5_Factors_2x3_CSV")
#FFdownload::FFdownload(output_file = "FF.RData",exclude_daily=TRUE,inputlist=inputlist)
load("FF.RData")


data_ml <- data_ml %>% select(-R3M_Usd,-R6M_Usd,-R12M_Usd)
stock_ids <- levels(as.factor(data_ml$stock_id)) 
stock_days <- data_ml %>%                        
    group_by(stock_id) %>% summarize(nb = n()) 
stock_ids_short <- stock_ids[which(stock_days$nb == max(stock_days$nb))] 

features <- colnames(data_ml[3:95]) 

#Preparing data with stock that have full data (no missing values)
data_predef_stocks <- process_data(data=data_ml, 
                                   stock_id_column="stock_id",
                                   feature_names=NULL,  
                                   label_name="R1M_Usd", 
                                   use_full_data_stocks=TRUE)

#Short refers to shorter list of stocks - predefined list of stocks that have no missing values.
data_short_wide <- data_predef_stocks$features_wide
returns_short <- data_predef_stocks$returns_winsorized
returns_short_test <- data_predef_stocks$returns_short_test

#Preparing data with all stock available
data_all_stocks <- process_data(data=data_ml, 
                                stock_id_column="stock_id",
                                feature_names=NULL,  
                                label_name="R1M_Usd", 
                                use_full_data_stocks=FALSE)


data_all_wide <- data_all_stocks$features_wide
returns_all <- data_all_stocks$returns_winsorized
returns_all_test <- data_all_stocks$returns

#data_all_wide_imputed <- impute_rowwise(data_all_wide, FUN=median,features)
load("~/R/Deep_Portfolio/data_all_wide_imputed.RData")
returns_all_imputed <- returns_all %>% mutate_all(impute_returns) 

FF_factors <- FFdata$`x_F-F_Research_Data_5_Factors_2x3`$monthly$Temp2 %>%
  timetk::tk_tbl(rename_index="date") %>% 
  mutate(across(Mkt.RF:RF,~./100),date=as.Date(date, frac=1)) %>%
  filter(date >= as.Date(min(data_all_stocks$dates)), date <= as.Date(max(data_all_stocks$dates)))

```

# Definition of The Training-Testing-Validation Sample Periods: 
```{r}
n_stock_selected <- length(stock_ids_short)

num_features <- ncol(data_short_wide)
val_window <- 60
training_window <- 60
first_test <- val_window + training_window

testing_period_len <-  nrow(data_short_wide)-training_window-val_window
testing_periods_seq <- seq(training_window, training_window+testing_period_len)
end_test <- first_test+testing_period_len
#max possible nrow(data_short_wide)-training_window-val_window


```


# Results of The Bayesian Optimisation: Neural Network Parameters
```{r}
activation_nl_i <- "sigmoid"
activation_conc <- "tanh"
learning_rate <-0.1
activation_nl_ii <-"swish"
units_choice <- 15
epochs <- 50
rate <- 0.1
batch_size <- 12

```
# NN with Complex Model with NLinear and Linear Layers
```{r, warning=FALSE, message=FALSE}
illustration_model_complex <- build_model(length(stock_ids_short), rate, units_choice, 
                         activation_nl_i,activation_conc,learning_rate, 
                         activation_nl_ii, data_short_wide,sharpe_ratio_loss)
summary(illustration_model_complex)
```

```{r, warning=FALSE}

illustration_model_lstm <- build_lstm_model(n_stocks, rate, units_choice,
                               learning_rate, data_2short_lstm_feat, loss = sharpe_ratio_loss,timesteps=12)
summary(illustration_model_lstm)
```



#Backtesting with all features
## Predefined number of stocks
### SR
#### Complex

```{r}
backtest_res_predef_ret_sr <- map(testing_periods_seq, backtest, data_short_wide, returns_short, 
                        model="complex", window="expand", stocks_preselected=TRUE, 
                        transaction_cost=FALSE)

performance_predef_sr <- generate_performance_metrics(backtest_res_predef_ret_sr, TRUE, returns_short)
performance_predef_sr$table

```

```{r}
plot_predef_sr <-plot_cumulative(backtest_res_predef_ret_sr, returns_short)
plot_predef_sr
```

#### LSTM

```{r}
learning_rate <-0.1
units_choice <- 10
epochs <- 50

backtest_predef_lstm_sr <- map(testing_periods_seq, backtest, data_short_wide, returns_short, 
                        model="lstm", window="expand", stocks_preselected=TRUE, 
                        transaction_cost=FALSE)

perform_predef_lstm <- generate_performance_metrics(backtest_predef_lstm_sr, TRUE, returns_short)
perform_predef_lstm
```

```{r}
plot_predef_lstm_sr <-plot_cumulative(backtest_predef_lstm_sr, returns_short, stock_preselected = TRUE)
plot_predef_lstm_sr
```

### SR TC Adj.
#### Complex
```{r}

backtest_predef_res_sr_tc <- map(testing_periods_seq, backtest, data_short_wide, returns_short,model="complex", 
                                 window="expand",stocks_preselected=TRUE,
                                 transaction_cost=TRUE)

performance_predef_sr_tc <- generate_performance_metrics(backtest_predef_res_sr_tc, TRUE, returns_short)
performance_predef_sr_tc
```
```{r, warning=FALSE}
plot_predef_res_sr_tc <-plot_cumulative(backtest_predef_res_sr_tc,TRUE, returns_short)
plot_predef_res_sr_tc
```


##  All stocks available
### SR loss:
#### Complex NN
```{r}
backtest_all_res_sr <- map(testing_periods_seq, backtest, data_all_wide_imputed, 
                                 returns_all_imputed,model="complex", window="expand", 
                                 stocks_preselected=FALSE, transaction_cost=FALSE)

performance_all_sr <- generate_performance_metrics(backtest_all_res_sr, FALSE, returns_all_imputed)
performance_all_sr
```
```{r}
plot_all_sr_tc <-plot_cumulative(backtest_all_res_sr, returns_all_imputed, stock_preselected = FALSE)
plot_all_sr_tc
```

#### LSTM
```{r}
backtest_all_lstm_sr <- map(testing_periods_seq, backtest, data_all_wide_imputed, returns_all_imputed, 
                        model="lstm", window="expand", stocks_preselected=FALSE, 
                        transaction_cost=FALSE)

performance_all_lstm_sr <- generate_performance_metrics(backtest_all_lstm_sr, FALSE, returns_all_imputed)
performance_all_lstm_sr

```
```{r}
plot_all_lstm_sr <-plot_cumulative(backtest_all_lstm_sr, returns_all_imputed, stock_preselected = FALSE)
plot_all_lstm_sr
```

###  SR TC Adj.:
#### Complex
```{r}
backtest_all_res_sr_tc <- map(testing_periods_seq, backtest, data_all_wide_imputed, 
                                 returns_all_imputed,model="complex", window="expand", 
                                 stocks_preselected=FALSE, transaction_cost=TRUE)

performance_all_sr_tc <- generate_performance_metrics(backtest_all_res_sr_tc, FALSE, returns_all_imputed)
performance_all_sr_tc

```

# Backtesting Size and Momentum features:

```{r}
features_two <-c("Mkt_Cap_3M_Usd", "Mom_11M_Usd")

data_2feat <- process_data(data=data_ml, 
                                   stock_id_column="stock_id",
                                   feature_names=features_two,  
                                   label_name="R1M_Usd", 
                                   use_full_data_stocks=TRUE)

data_2short_wide <- data_2feat$features_wide
returns_2short <- data_2feat$returns_winsorized
returns_2short_test <- data_2feat$returns_short_test
```
# SR
```{r}
backtest_2predef <- map(testing_periods_seq, backtest, data_2short_wide, returns_2short, 
                        model="simple", window="expand", stocks_preselected=TRUE, 
                        transaction_cost=FALSE)

performance_2predef <- generate_performance_metrics(backtest_2predef, TRUE, returns_2short)
performance_2predef
```
```{r}
plot_cumulative(backtest_2predef, returns_2short)
```

# Backtesting with predefined stocks and Size and Momentum features with SR loss TC Adj.:
## Backtesting with predefined number of stocks
### SR

#### Complex


#### Simple


#### LSTM

```{r}
backtest_predef_lstm_2feat <- map(testing_periods_seq, backtest, data_2short_wide, returns_2short, 
                        model="lstm", window="expand", stocks_preselected=TRUE, 
                        transaction_cost=FALSE)

performance_predef_lstm_2feat <- generate_performance_metrics(backtest_predef_lstm_2feat, TRUE, returns_2short)
performance_predef_lstm_2feat
```

```{r}
plot_cumulative(backtest_predef_lstm_2feat, returns_2short)
```


### SR TC Adj.
#### Simple

```{r}
backtest_2predef_ret_sr_tc <- map(testing_periods_seq, backtest, data_2short_wide, returns_2short, 
                        model="simple", window="expand", stocks_preselected=TRUE, 
                        transaction_cost=TRUE)

performance_3predef_sr_tc <- generate_performance_metrics(backtest_2predef_ret_sr_tc, TRUE, returns_2short)
performance_3predef_sr_tc

```

```{r}
plot_cumulative(backtest_2predef_ret_sr_tc, returns_2short)
```

#### Complex

```{r}
# Create an instance of the Backtest class
m10 <- Backtest$new(data_2short_wide, returns_2short, model="complex", transaction_cost=TRUE, stocks_preselected=TRUE)

# Call the print method
m10$print()
```

#### LSTM

## Backtesting with all stocks available
### SR

#### Complex


#### Simple


#### LSTM

### SR TC Adj.

#### Complex


#### Simple


#### LSTM
training according to optimum weights